Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2019-08-16 peakcharacterization_manuscript.Rmd
added all the authors and changed output type to PDF until we can get next version of fedora installed

---
title: "Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments"
author: "Robert M Flight"
date: "`r Sys.time()`"
commit: "`r substr(git2r::branch_target(git2r::head(git2r::repository())), 1, 8)`"
output: 
  redoc::redoc
---

>>>>

---
title: "Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments"
author: "Robert M Flight, Joshua M Mitchell, Hunter NB Moseley"
date: "`r Sys.time()`"
commit: "`r substr(git2r::branch_target(git2r::head(git2r::repository())), 1, 8)`"
output: 
  pdf_document
---
